Artin Group Presentations Arising from Cluster Algebras

### 2014-08-14 Paper.tex
added changes suggested by Gregg

Using this group presentation, Barot and Marsh state the following result:
\begin{thm}\cite[Theorem A]{BM13}
Let $\Gamma$ be the diagram associated to a seed in a cluster algebra of finite type. Then $W(\Gamma)$ is isomorphic to the corresponding reflection group.
\end{thm}

@@

\begin{prop}
\label{cycle_types}
\cite[Proposition 2.1]{BM13} Let $\Gamma$ be a diagram of finite type. Then, a chordless cycle in the unoriented graph of $\Gamma$ is cyclically oriented in $\Gamma$. Furthermore, the unoriented graph underlying the cycle must either be a cycle such that all edges have weight 1, a square with two opposite edges of weight 2 and two opposite edges of weight 1, or a triangle with two edges of weight 2 and one of weight 1, as pictured below.
\\
\hspace*{-1.2cm}
\begin{tikzpicture}[baseline=-0.5ex]
 \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
  {
    & &|[name = ul]|\circ& |[name = ur]|\circ&\\
    %
    &|[name=lu]| \circ &&&|[name=ru]| \circ \\
     & |[name = ld]|\circ&&& |[name = rd]|\circ\\
    %
    &&|[name=dl]| \circ &|[name=dr]| \circ &\\
  };
\draw
  (ul) -- node[above] {1} (ur)
  ;
  \draw
  (ul) -- node[left]{1}(lu)
  ;
  \draw
  (dr) -- node[right]{1}(rd)
  ;
  \draw
  (lu) -- node[left]{1}(ld)
  ;
  \draw
  (ru) -- node[right]{1}(rd)
  ;
  \draw
  (ur) -- node[right]{1}(ru)
  ;
  \draw
  (dl) -- node[left]{1}(ld)
  ;
  \draw[dotted]
  (dl) -- (dr)
  ;
 \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (5,0)
  {
    & |[name = ul]|\circ& |[name = ur]|\circ\\
    %
    &|[name=dl]| \circ &|[name=dr]| \circ \\
  };
\draw
  (ul) -- node[above] {1} (ur)
  ;
  \draw
  (dl) -- node[left]{2}(ul)
  ;
  \draw
  (dr) -- node[below]{1}(dl)
  ;
  \draw
  (ur) -- node[right]{2} (dr)
  ;
   \matrix[matrix of math nodes,column sep={25pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (9,0)
  {
    && |[name = u]|\circ& \\
    %
    &|[name=dl]| \circ & &|[name=dr]| \circ \\
  };
\draw
  (u) -- node[right] {2} (dr)
  ;
  \draw
  (dl) -- node[left]{2}(u)
  ;
  \draw
  (dr) -- node[below]{1}(dl)
  ;

\end{prop}

@@

@@

@@

\item We have
\begin{align*}
s_2^{-1}t^\prime(3,1)s_2 &= s_2^{-1}t_3t_1^{-1}t_2t_1t_3^{-1}t_1^{-1}s_2^{-1}t_1s_2\\
&= s_3\underline{s_2^{-1}s_1^{-1}s_2s_1s_2}s_3^{-1}\underline{s_2^{-1}s_1^{-1}s_2^{-1}s_1s_2}\\
&= s_3s_1\underline{s_2s_1^{-1}s_3^{-1}s_1}s_2^{-1}s_1^{-1}\\
&= s_3s_1s_1^{-1}s_3^{-1}s_1s_2s_2^{-1}s_1^{-1} &t(2,1)\\
&= e
\end{align*}

@@

\item We have
\begin{align*}
t_1t_2^{-1}t_3^{-1}t_4t_3t_2 &= (s_1s_2^{-1}s_1^{-1}s_1s_2s_1^{-1})s_1s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3s_1s_2s_1^{-1}\\
&= s_1s_2^{-1}s_1^{-1}\underline{s_1s_2s_1s_2^{-1}s_1^{-1}}s_3^{-1}s_4s_3s_1s_2s_1^{-1}\\
&= s_1s_2^{-1}s_1^{-1}\underline{s_2s_3^{-1}s_4s_3}s_1s_2s_1^{-1}\\
&= s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3\underline{s_2s_1s_2s_1^{-1}} &t(2,3)\\
&= s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3s_1s_2s_1^{-1}s_1\\
&= t_2^{-1}t_3^{-1}t_4t_3t_2t_1\\
\end{align*}

@@

\item We have
\begin{align*}
t_1t_2^{-1}t_3^{-1}t_4t_3t_2 &= s_1\underline{s_2^{-1}s_2}s_3^{-1}\underline{s_2^{-1}s_4s_2}s_3 \underline{s_2^{-1}s_2}\\
&= s_1s_3^{-1}s_4s_3\\
&= s_3^{-1}s_4s_3s_1 &t(1,3)\\
&= (s_2^{-1}s_2)s_3^{-1}(s_2^{-1}\underline{s_2)s_4(s_2^{-1}}s_2)s_3(s_2^{-1}s_2s_1\\
&= s_2^{-1}s_2s_3^{-1}s_2^{-1}s_4s_2s_3s_2^{-1}s_2s_1\\
&= t_2^{-1}t_3^{-1}t_4t_3t_2t_1\\
\end{align*}

@@

\item We have
\begin{align*}
t_3t_4^{-1}t_1t_4 &= s_3s_4^{-1}\underline{s_2s_1s_2^{-1}}s_4\\
&= s_3s_4^{-1}s_1^{-1}s_2s_1s_4\\
&= s_4^{-1}\underline{s_1^{-1}s_2s_1}s_4s_3 &t(3,4)\\
&= s_4^{-1}s_2s_1s_2^{-1}s_4s_3\\
&= t_4^{-1}t_1t_4t_3\\
\end{align*}

@@

\begin{align*}
t_1t_2^{-1}\cdots t_{h-1}^{-1}t_ht_{h-1}\cdots t_2 &= s_1s_2^{-1}\cdots s_{h-1}^{-1}s_ks_hs_k^{-1}s_{h-1}\cdots s_2\\
&= s_k\underline{s_1s_2^{-1}\cdots s_{h-1}^{-1}s_hs_{h-1}\cdots s_2}s_k^{-1}\\
&= s_ks_2^{-1}\cdots s_{h-1}^{-1}s_hs_{h-1}\cdots s_2s_1s_k^{-1} &t(1,2)\\
&= s_2^{-1}\cdots s_{h-1}^{-1}s_ks_hs_k^{-1}s_{h-1}\cdots s_2s_1\\
&= t_2^{-1}\cdots t_{h-1}^{-1}t_ht_{h-1}\cdots t_2t_1\\
\end{align*}

>>>>

Using this group presentation, Barot and Marsh state the following result:
\begin{thm}\label{thm:barot_and_marsh_A}\cite[Theorem A]{BM13}
Let $\Gamma$ be the diagram associated to a seed in a cluster algebra of finite type. Then $W(\Gamma)$ is isomorphic to the corresponding reflection group.
\end{thm}

@@

\begin{prop}
\label{cycle_types}
\cite[Proposition 2.1]{BM13} Let $\Gamma$ be a diagram of finite type. Then, a chordless cycle in the unoriented graph of $\Gamma$ is cyclically oriented in $\Gamma$. Furthermore, the unoriented graph underlying the cycle must either be a cycle such that all edges have weight 1, a square with two opposite edges of weight 2 and two opposite edges of weight 1, or a triangle with two edges of weight 2 and one of weight 1, as pictured in Figure \ref{fig:cycle_types}

\begin{figure}[h]\label{fig:cycle_types}
\hspace*{-1.2cm}
\begin{tikzpicture}[baseline=-0.5ex]
 \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
  {
    & &|[name = ul]|\circ& |[name = ur]|\circ&\\
    %
    &|[name=lu]| \circ &&&|[name=ru]| \circ \\
     & |[name = ld]|\circ&&& |[name = rd]|\circ\\
    %
    &&|[name=dl]| \circ &|[name=dr]| \circ &\\
  };
\draw
  (ul) -- node[above] {1} (ur)
  ;
  \draw
  (ul) -- node[left]{1}(lu)
  ;
  \draw
  (dr) -- node[right]{1}(rd)
  ;
  \draw
  (lu) -- node[left]{1}(ld)
  ;
  \draw
  (ru) -- node[right]{1}(rd)
  ;
  \draw
  (ur) -- node[right]{1}(ru)
  ;
  \draw
  (dl) -- node[left]{1}(ld)
  ;
  \draw[dotted]
  (dl) -- (dr)
  ;
 \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (5,0)
  {
    & |[name = ul]|\circ& |[name = ur]|\circ\\
    %
    &|[name=dl]| \circ &|[name=dr]| \circ \\
  };
\draw
  (ul) -- node[above] {1} (ur)
  ;
  \draw
  (dl) -- node[left]{2}(ul)
  ;
  \draw
  (dr) -- node[below]{1}(dl)
  ;
  \draw
  (ur) -- node[right]{2} (dr)
  ;
   \matrix[matrix of math nodes,column sep={25pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (9,0)
  {
    && |[name = u]|\circ& \\
    %
    &|[name=dl]| \circ & &|[name=dr]| \circ \\
  };
\draw
  (u) -- node[right] {2} (dr)
  ;
  \draw
  (dl) -- node[left]{2}(u)
  ;
  \draw
  (dr) -- node[below]{1}(dl)
  ;

   \end{tikzpicture}
\caption{Possible chordless cycles in a diagram of finite type}
\end{figure}
\end{prop}

@@

The structure of the proof will be analogous to the structure of the proof of Theorem \ref{thm:barot_and_marsh_A}, but with most of the details changed to account for the fact that the $(R1)$ relations are not included.  In particular, many of the computations used to prove the supporting lemmas and propositions of Theorem \ref{thm:barot_and_marsh_A} rely heavily on the $(R1)$ relations and therefore did not apply to the supporting lemmas and propositions of Theorem \ref{thm:main}.

@@

In other words, starting at any node in the square below and following the maps around gives the identity map.

\begin{figure*}[h]
\hspace*{-4em}
\begin{tikzpicture}[baseline=-0.5ex]
\matrix[matrix of math nodes,column sep={60pt,between origins},row
    sep={60pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
  {
    & |[name = ul]|{A_{\Gamma^{op}}}\circ& |[name = ur]|\circ{A_{\left(\Gamma^\prime\right)^{op}}}\\
    %
    &|[name=dl]|{A_{\Gamma}} \circ &|[name=dr]| \circ{A_{\Gamma^\prime}} \\
  };
\draw[->]
  (ul) to node[above]{$\varphi_{op}$} (ur)
  ;
  \draw[->]
  (dl) to node[left]{$\Delta$}(ul)
  ;
  \draw[->]
  (dr) to node[below]{$\varphi$}(dl)
  ;
  \draw[->]
  (ur) to node[right]{$\Gamma^\prime$} (dr)
  ;
\end{tikzpicture}
\end{figure*}

@@

\item We have
\begin{align*}
s_2^{-1}t^\prime(3,1)s_2 &= s_2^{-1}t_3t_1^{-1}t_2t_1t_3^{-1}t_1^{-1}s_2^{-1}t_1s_2\\
&= s_3\underline{s_2^{-1}s_1^{-1}s_2s_1s_2}s_3^{-1}\underline{s_2^{-1}s_1^{-1}s_2^{-1}s_1s_2}\\
&= s_3s_1\underline{s_2s_1^{-1}s_3^{-1}s_1}s_2^{-1}s_1^{-1}\\
&= s_3s_1s_1^{-1}s_3^{-1}s_1s_2s_2^{-1}s_1^{-1} &\text{by } t(2,1)\\
&= e
\end{align*}

@@

\item We have
\begin{align*}
t_1t_2^{-1}t_3^{-1}t_4t_3t_2 &= (s_1s_2^{-1}s_1^{-1}s_1s_2s_1^{-1})s_1s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3s_1s_2s_1^{-1}\\
&= s_1s_2^{-1}s_1^{-1}\underline{s_1s_2s_1s_2^{-1}s_1^{-1}}s_3^{-1}s_4s_3s_1s_2s_1^{-1}\\
&= s_1s_2^{-1}s_1^{-1}\underline{s_2s_3^{-1}s_4s_3}s_1s_2s_1^{-1}\\
&= s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3\underline{s_2s_1s_2s_1^{-1}} &\text{by } t(2,3)\\
&= s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3s_1s_2s_1^{-1}s_1\\
&= t_2^{-1}t_3^{-1}t_4t_3t_2t_1\\
\end{align*}

@@

\item We have
\begin{align*}
t_1t_2^{-1}t_3^{-1}t_4t_3t_2 &= s_1\underline{s_2^{-1}s_2}s_3^{-1}\underline{s_2^{-1}s_4s_2}s_3 \underline{s_2^{-1}s_2}\\
&= s_1s_3^{-1}s_4s_3\\
&= s_3^{-1}s_4s_3s_1 &\text{by } t(1,3)\\
&= (s_2^{-1}s_2)s_3^{-1}(s_2^{-1}\underline{s_2)s_4(s_2^{-1}}s_2)s_3(s_2^{-1}s_2s_1\\
&= s_2^{-1}s_2s_3^{-1}s_2^{-1}s_4s_2s_3s_2^{-1}s_2s_1\\
&= t_2^{-1}t_3^{-1}t_4t_3t_2t_1\\
\end{align*}

@@

\item We have
\begin{align*}
t_3t_4^{-1}t_1t_4 &= s_3s_4^{-1}\underline{s_2s_1s_2^{-1}}s_4\\
&= s_3s_4^{-1}s_1^{-1}s_2s_1s_4\\
&= s_4^{-1}\underline{s_1^{-1}s_2s_1}s_4s_3 &\text{by} t(3,4)\\
&= s_4^{-1}s_2s_1s_2^{-1}s_4s_3\\
&= t_4^{-1}t_1t_4t_3\\
\end{align*}

@@

\begin{align*}
t_1t_2^{-1}\cdots t_{h-1}^{-1}t_ht_{h-1}\cdots t_2 &= s_1s_2^{-1}\cdots s_{h-1}^{-1}s_ks_hs_k^{-1}s_{h-1}\cdots s_2\\
&= s_k\underline{s_1s_2^{-1}\cdots s_{h-1}^{-1}s_hs_{h-1}\cdots s_2}s_k^{-1}\\
&= s_ks_2^{-1}\cdots s_{h-1}^{-1}s_hs_{h-1}\cdots s_2s_1s_k^{-1} &\text{by } t(1,2)\\
&= s_2^{-1}\cdots s_{h-1}^{-1}s_ks_hs_k^{-1}s_{h-1}\cdots s_2s_1\\
&= t_2^{-1}\cdots t_{h-1}^{-1}t_ht_{h-1}\cdots t_2t_1\\
\end{align*}
